Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2021-12-15 jas_response.tex
minor edits to the response by TL

The primary benefit of the dumbbell approximation is to avoid the additional integral over the entire body.
While conceptually and analytically simple the dumbbell model still captures the important rigid body effects on the system, namely the coupling of attitude and translational states through the external forces and moments.
In addition, this type of spacecraft model is prevelant in the field~\cite{kulumani2017b,lee2006a,lee2007a,elmasri2005}.
Additional comments have been added to the manuscript explaining this decision and copied here.

@@

Specific comments:
}

@@

Thank you for this comment. 
We have replaced ''dynamic`` with ''dynamical`` in several locations throughout the manuscript.
We do not repeat the corrections here for simplicity.

@@

This sentence has been removed and replaced with the following:

@@

\comment{
Page 8, line 1-2, the authors should augment the statement made citing reference 7 with one or two sentences for the unfamiliar reader.  
}
Additional detail describing the polyhedron potential model is added and copied below.

@@

More recent references from the OSIRIS-REx mission have been included and additional discussion is copied below.

@@

The equation has been corrected and is copied below.

@@

\begin{correction}
    In this numerical example we have assumed perfect state knowledge of the spacecraft.
    This is a strong assumption that would not exist in any realistic situation. 
    However, the measurement model defined in the previous section may be extended to consider the uncertainty in both the state \( x \) and the range measurement \( d \) rather than combining them into a single random variable \( p \).
    In addition, the dynamics defined by~\crefrange{eq:x_dot}{eq:omega_dot} do not consider any non-gravitational accelerations such as solar radiation pressure on the vehicle.
    In general, these types of external forces will primarily serve to increase state uncertainty and cause large errors in the closed loop control system.
    Adaptive control techniques have been demonstrated in the past to address both fixed and time varying disturbances of this kind~\cite{kulumani2017a}.
    The authors will relax these assumptions in future work.
\end{correction}

@@

The guidance scheme presented in~\cref{sec:explore_asteroid} will drive the vehicle towards states which will best reduce the total uncertainty of the shape model.
As a result the vehicle in general may take an arbitrary trajectory about the body and utilize much larger control effort compared to utilizing the natural dynamics of the system. 
We do not duplicate the motion of Hayabusa but did utilize the ''home position`` term to describe the numerical example.
Our shape refinement approach is not limited to our guidance scheme but rather is an example of combining closed loop control with our shape refinement method.
We will consider incorporating control effort constraints in our optimal guidance scheme in a future work.

@@

\comment{
As part of section 5, the authors should discuss impacts of more complex criteria for landing or surface sampling, for instance, types of material on the surface, poles versus equatorial areas, etc. 
It may be good to look at sampling requirements and criteria of recent missions to see how they would affect the technique described.
}
Our landing site selection algorithm is relatively simple as it is a direct function of the shape model.
The approach was chosen as an example to demonstrate how a vehicle can autonomously model the shape of the asteroid, then utilize that shape model to chose a landing site. 
Additional costs such as surface material or location on the body can be added as additional criteria in~\cref{eq:surface_cost}.
We have added additional discussion concerning the landing site selection approach.

>>>>

The motivation is to capture the effects of the relative attitude between spacecraft and asteroid on the corresponding gravitational force and moment. 
The primary benefit of the dumbbell approximation is that the additional integral over the entire body is avoided. 
While conceptually and analytically simple the dumbbell model still captures the important rigid body effects on the system, namely the coupling of attitude and translational states through the external forces and moments.
In addition, this type of spacecraft model is prevelant in the field~\cite{kulumani2017b,lee2006a,lee2007a,elmasri2005}.
To clarify these, additional comments have been added to the manuscript explaining this decision and copied here.

@@

%Specific comments:
}

@@

Thank you for this comment. 
We have replaced ``dynamic'' with ``dynamical'' in several locations throughout the manuscript.
We do not repeat the corrections here for simplicity.

@@

Thank you for the comment.
This sentence has been removed and replaced with the following:

@@

\comment{
Page 8, line 1-2, the authors should augment the statement made citing reference 7 with one or two sentences for the unfamiliar reader.  
}

Additional detail describing the polyhedron potential model is added and copied below.

@@

More recent references from the OSIRIS-REx mission have been included and additional discussion is added as copied below.

@@

The equation has been corrected and is copied below.
The code has been rechecked.

@@

\begin{correction}
    In this numerical example we have assumed the perfect knowledge of the spacecraft state. 
    This is a strong assumption that would not exist in any realistic situation. 
    However, the measurement model defined in the previous section may be extended to consider the uncertainty in both the state \( x \) and the range measurement \( d \) rather than combining them into a single random variable \( p \).
    In addition, the dynamics defined by~\crefrange{eq:x_dot}{eq:omega_dot} do not consider any non-gravitational accelerations such as solar radiation pressure on the vehicle.
    In general, these types of external forces will primarily serve to increase state uncertainty and cause large errors in the closed loop control system.
    Adaptive control techniques have been demonstrated in the past to address both fixed and time varying disturbances of this kind~\cite{kulumani2017a}.
    However, these topics are beyond the scope of this paper focusing on optimal guidance for Bayesian shape reconstruction, and relegated to future works. 
\end{correction}

@@

The guidance scheme presented in~\cref{sec:explore_asteroid} will drive the vehicle towards states which will best reduce the total uncertainty of the shape model.
As a result the vehicle in general may take an arbitrary trajectory about the body and utilize much larger control effort compared to utilizing the natural dynamics of the system. 
We do not duplicate the motion of Hayabusa but did utilize the ``home position'' term to describe the numerical example.
Our shape refinement approach is not limited to our guidance scheme but rather is an example of combining closed loop control with our shape refinement method.
We will consider incorporating control effort constraints in our optimal guidance scheme in a future work.

@@

\comment{
As part of section 5, the authors should discuss impacts of more complex criteria for landing or surface sampling, for instance, types of material on the surface, poles versus equatorial areas, etc. 
It may be good to look at sampling requirements and criteria of recent missions to see how they would affect the technique described.
}

Our landing site selection algorithm is relatively simple as it is directly evaluated by the shape model.
The approach was chosen as an example to demonstrate how a vehicle can autonomously model the shape of the asteroid, then utilize that shape model to chose a landing site. 
Additional costs such as surface material or location on the body can be added as additional criteria in~\cref{eq:surface_cost}.
We have added additional discussion concerning the landing site selection approach.
